Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010

### 2017-08-06 ms.tex
finished referee comments on conclusions.

We obtained high precision ground-based spectrophotometry of two brown dwarfs of spectral type L4-L5: {\sha} and {\shb}.
These brown dwarfs have temperatures near the condensation temperature of forsterite (Mg$_2$SiO$_4$).
We find that {\sha} has marginal variability and no significant wavelength dependence; while
{\shb} shows significant variability up to the 1.5\% amplitude (3.0\% peak-to-valley) at short wavelengths (0.9~$\mu$m) which declines towards the near infrared (2.4$~\mu$m).
A possible difference between the two brown dwarfs is the viewing geometry with \sha\ closer to pole-on and \shb\ closer to equator-on as shown in Table \ref{tab:bdProp}.
Recently, \citet{vos2017viewingGeom} find that there are correlations between variability and color properties as a function of viewing geometry and that equator-on dwarfs show, on average, larger variability amplitudes.

@@

Using ground-based facilities such as SpeX on IRTF allows us to expand our monitoring of cloud-bearing ultracool dwarfs, both in sample size and long-term tracking. The former can provide powerful constraints on how dust particle sizes may depend on differing pressure-temperature profiles, rotation rates, composition and viewing orientations; while the latter allows us to study weather-related changes to cloud structures over multiple rotation periods. We are currently pursuing a larger monitoring sample that will be reported in future publications.

@@

\textbf{\software{\texttt{emcee} \citep{foreman-mackey2013emcee}, \texttt{corner.py} \citep{foremanCorner}. SpeX Prism Library Analysis Toolkit \citep{2017arXiv170700062B}, \texttt{astropy} \citep{astropy2013}.\texttt{IRAF} \citep{tody86}, \texttt{IDL} version 8.5 (Exelis Visual Information Solutions, Boulder, Colorado)}}

>>>>

We obtained high precision ground-based spectrophotometry of two brown dwarfs of spectral \textbf{types} L4-L5: {\sha} and {\shb}.
These brown dwarfs have temperatures near the condensation temperature of forsterite (Mg$_2$SiO$_4$).
We find that {\sha} has marginal variability and no significant wavelength dependence; while
{\shb} shows significant variability up to the 1.5\% amplitude (3.0\% peak-to-valley) at short wavelengths (0.9~$\mu$m) which declines towards the near infrared (2.4$~\mu$m).
A possible difference between the two brown dwarfs is the viewing geometry with \sha\ closer to pole-on and \shb\ closer to equator-on as shown in Table \ref{tab:bdProp}.
Recently, \citet{vos2017viewingGeom} find that there are correlations between variability and color properties as a function of viewing geometry and that equator-on dwarfs show, on average, larger variability amplitudes.
\textbf{\sha\ shows less variability than reported in the literature which shows at a tentative period of 3.1 hours \citep{2004MNRAS.354..378K,2014A&A...566A.111W}, so it likely exhibited a more homogeneous cloud distribution at our observed epoch.}

@@

Using ground-based facilities such as SpeX on IRTF allows us to expand our monitoring of cloud-bearing ultracool dwarfs, both in sample size and long-term tracking. The former can provide powerful constraints on how dust particle sizes may depend on differing pressure-temperature profiles, rotation rates, composition and viewing orientations \textbf{while} the latter allows us to study weather-related changes to cloud structures over multiple rotation periods. We are currently pursuing a larger monitoring sample that will be reported in future publications.

@@

\textbf{\software{
\texttt{emcee} \citep{foreman-mackey2013emcee},
\texttt{corner.py} \citep{foremanCorner},
\texttt{miescatter} \citep{bohren1983mie},
SpeX Prism Library Analysis Toolkit \citep{2017arXiv170700062B},
\texttt{astropy} \citep{astropy2013},
\texttt{IRAF} \citep{tody86} and
\texttt{IDL} version 8.5 (Exelis Visual Information Solutions, Boulder, Colorado)}}
